---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geckor

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/next-game-solutions/geckor/branch/main/graph/badge.svg)](https://codecov.io/gh/next-game-solutions/geckor?branch=main)
<!-- badges: end -->

The goal of geckor is to ...

## Installation

You can install the released version of geckor from [CRAN](https://CRAN.R-project.org) with:

``` r
#install.packages("geckor")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
#devtools::install_github("next-game-solutions/geckor")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(geckor)
## basic example code
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
