---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geckor

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/next-game-solutions/geckor/branch/main/graph/badge.svg)](https://codecov.io/gh/next-game-solutions/geckor?branch=main)
[![R-CMD-check](https://github.com/next-game-solutions/geckor/workflows/R-CMD-check/badge.svg)](https://github.com/next-game-solutions/geckor/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`geckor` is an R client for the public [CoinGecko API](https://www.coingecko.com/en/api#explore-api). This package implements a
number of major endpoints offered by that API and allows one to collect the
current and historical market data on over 7000 cryptocurrencies from more than 400 exchanges. Results are typically returned in a tabular form as tibbles, ready for any downstream analyses.

## Installation

At the moment, `geckor` is only available on GitHub and can be installed with:

``` r
# install.packages("devtools")
devtools::install_github("next-game-solutions/geckor")
```

## Examples

Detailed examples of how to use `geckor` can be found in its [online documentation](https://next-game-solutions.github.io/geckor/). Provided below are just a few common queries:


```{r example, message=FALSE, fig.align='center', fig.width=10, fig.height=4.5}
library(geckor)
library(dplyr)
library(ggplot2)

# Get the current price of Cardano, Tron, and Polkadot,
# expressed in USD, EUR, and GBP:
current_price(coin_ids = c("cardano", "tron", "plokadot"),
              vs_currencies = c("usd", "eur", "gbp"))

# Get a more comprehensive view of the current Cardano, Tron, and 
# Polkadot markets:
current_market(coin_ids = c("cardano", "tron", "polkadot"), 
               vs_currency = "usd") %>% 
  glimpse()

# Collect all historical data on the price of Cardano (expressed in EUR),
# and plot the result:
cardano_history <- coin_history(coin_id = "cardano", 
                                vs_currency = "eur", 
                                days = "max")

cardano_history %>% 
  ggplot(aes(timestamp, price)) +
  geom_line() + theme_minimal()
```

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/next-game-solutions/geckor/issues).


## License

This package is licensed to you under the terms of the MIT License.

Copyright (c) `r substr(as.Date(Sys.Date()), 1, 4)` [Next Game Solutions OÜ](http://nextgamesolutions.com)

---

Please note that this project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/1/0/0/code-of-conduct/). By participating in this project you agree to abide by its terms.
