---
title: "Current market data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Current market data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(geckor)
```

```{r libs, message=FALSE}
library(dplyr)
```

The CoinGecko API allows one to query market data on cryptocurrencies in real time. There are several functions in `geckor` that can be used to collect such data.

The current prices for a set of cryptocurrencies of interest can be queried with the `current_price()` function. The two important arguments expected by this function are `coin_ids` (a character vector with coin IDs; see `?supported_coins` for details) and `vs_currencies` (a character vector with abbreviated names of reference currencies, which are used to express the price in; see `?supported_currencies` for details). In the example below, we are requesting the current prices for Cardano, Tron, and Polkadot, expressed in USD, EUR, and GBP:

```{r current-price}
prices <- current_price(
  coin_ids = c("cardano", "tron", "polkadot"),
  vs_currencies = c("usd", "eur", "gbp")
)

prices
```

See `?current_price` for definitions of columns in the resultant tibble.

The `exchange_rate()` function can be used to obtain the current exchange rates for any supported reference currency, expressed in Bitcoin. The `currency` argument of this function specifies the list of currencies of interest. If `currency = NULL`, data for all supported currencies will be returned:

```{r exchange-rates}
all_rates <- exchange_rate(currency = NULL)
head(all_rates, 10)

some_rates <- exchange_rate(currency = c("btc", "usd", "rub"))
some_rates
```

The `current_market()` function retrieves a rich set of data points describing the current market status of the cryptocurrencies of interest. Let's collect such data for Cardano, Tron, and Polkadot:

```{r current-market}
cm <- current_market(
  coin_ids = c("cardano", "tron", "polkadot"),
  vs_currency = "usd"
)

glimpse(cm)
```

See `?current_market` for definitions of columns in the resultant tibble.

The `coin_tickers()` function allows one to query the current data on all trading pairs of a cryptocurrency from a given exchange. In the example below, we collect such data for Cardano traded at Binance:

```{r coin-tickers}
cardano_tickers <- coin_tickers(
  coin_id = "cardano",
  exchange_id = "binance"
)

glimpse(cardano_tickers)
```

See `?coin_tickers` for definitions of columns in the resultant tibble.

Finally, one can use the `trending_coins()` function to obtain a list of top-7 trending coins in terms of their search popularity on CoinGecko:

```{r trending-coins}
trending_coins()
```
