---
title: "Historical market data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Historical market data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(geckor)
```

There are several functions in `geckor` that can retrieve historical market data for cryptocurrencies. All of these functions have the "`coin_history`" prefix in their names. In all of the examples described below, we will be collecting historical data for Bitcoin.

Coin-specific market data for a given historical date can be obtained using the `coin_history_snapshot()` function:

```{r snapshot}
coin_history_snapshot(
  coin_id = "bitcoin",
  date = as.Date("2021-01-01"),
  vs_currencies = c("usd", "eur", "gbp")
)
```

The `coin_history_range()` function can be used to query a range of historical dates (specified by the `from` and `to` arguments, which expect POSIXct timestamps). The granularity of the returned data depends on the requested range. Hourly data will be retrieved for periods of up to 90 days, and daily data for periods that are longer than 90 days:

```{r date-range}
# Range of less than 1 day:
coin_history_range(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  from = as.POSIXct("2020-01-01 10:00:10"),
  to = as.POSIXct("2020-01-01 20:45:10")
)

# Range of >90 days:
coin_history_range(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  from = as.POSIXct("2021-01-01 00:00:00"),
  to = as.POSIXct("2021-05-01 00:00:00")
)
```

To retrieve historical data from the last *n* days only, use the `coin_history()`:

```{r last-n-days}
coin_history(
  coin_id = "bitcoin",
  vs_currency = "usd",
  days = 7
)
```

In addition to numeric values, the `days` argument also accepts a character value `"max"`, which results in retrieving the entire existing history of market data for a coin (*please note:* querying the entire history can take some time):

```{r all-history}
coin_history(
  coin_id = "bitcoin",
  vs_currency = "usd",
  days = "max"
)
```

Notice the different data granularity in the last two examples. Generally, if `days = 1` the data will be presented for approximately every 3-8 minutes. If `days` is between 2 and 90 (inclusive), an hourly time step will be used. Daily data are used for `days` above 90. One can use the `interval` argument to control this granularity (by default, `interval = NULL`). However, at the moment the only value it accepts is `"daily"`:

```{r interval-usage}
# Within-day data, with `interval = "daily"`:
coin_history(
  coin_id = "bitcoin",
  vs_currency = "usd",
  days = 1, 
  interval = "daily"
)

# Less than 90 days, with `interval = "daily"`:
coin_history(
  coin_id = "bitcoin",
  vs_currency = "usd",
  days = 10, 
  interval = "daily"
)

# More than 90 days, with `interval = "daily"`:
coin_history(
  coin_id = "bitcoin",
  vs_currency = "usd",
  days = 100, 
  interval = "daily"
)
```

The open-high-low-close ([OHLC](https://en.wikipedia.org/wiki/Open-high-low-close_chart)) data characterise within-date and between-date price movements of a financial asset. In `geckor`, this type of data can be retrieved using the `coin_history_ohlc()` function, which has the same arguments as `coin_history()`, except for not having the `interval` argument. The granularity of the retrieved data (i.e. candle's body) depends on the value of `days` as follows:

-   1 day: 30 minutes

-   7 - 30 days: 4 hours

-   31 and above: 4 days

The only values currently accepted by the `days` argument are 1, 7, 14, 30, 90, 180, 365 and `"max"`. Here are some examples:

```{r ohlc}
# 30-minutes granularity:
coin_history_ohlc(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  days = 1
)

# 4-hours granularity:
coin_history_ohlc(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  days = 7
)

# 4-days granularity:
coin_history_ohlc(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  days = 90
)

# 4-days granularity:
coin_history_ohlc(
  coin_id = "bitcoin", 
  vs_currency = "usd",
  days = "max"
)
```
