---
title: "Supported coins, base currencies, and exchanges"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Supported coins, base currencies, and exchanges}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  error = TRUE,
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(geckor)
```

The [CoinGecko API](https://www.coingecko.com/en/api#explore-api "CoinGecko API") allows one to query market data on thousands of cryptocurrencies from hundreds of exchanges. You can obtain a list of the currently supported cryptocurrencies with the `supported_coins()` function:

```{r supported-coins}
coins <- supported_coins()

# number of supported coins:
nrow(coins)

head(coins, 10)
```

The first column in the resultant tibble contains coin IDs in the format expected by other `geckor` functions.

Similarly, you can retrieve a list of supported exchanges with the `supported_exchanges()` function:

```{r supported-exchanges}
exchanges <- supported_exchanges()

# number of supported exchanges:
nrow(exchanges)

head(exchanges, 10)
```

One of the important columns in the obtained tibble is `trust_score`. This score ranges from 1 to 10 and combines several metrics indicative of how much one can trust the data originating from a given exchange (see [this](https://blog.coingecko.com/trust-score/ "Trust Score v1") and [this](https://blog.coingecko.com/trust-score-2/ "Trust Score v2") articles on the CoinGecko website for details).

When querying market data for a cryptocurrency, users are always expected to supply one or several reference currencies (fiat or crypto) to express the coin price. You can retrieve the list of such reference currencies with the `supported_currencies()` function:

```{r supported-currencies}
currencies <- supported_currencies()
print(currencies)
```
